Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-02 MultipleRoundSims/sections/05-results1.tex
.9 and .25 for 05-results1.tex
changed figure size

\begin{figure}
\includegraphics[width=0.8\textwidth]{eor_bravo_90perc_10^4_corrected/sprob_first_three_cropped.png}\caption{
This plot shows, for each state margin, when the underlying election is as announced, the number of EoR \BRAVO audits that stopped in the $j^{th}$ round,
as a fraction of all EoR \BRAVO audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$.}
\label{fig:eor_bravo_sprob}
\end{figure}

\begin{figure}
\includegraphics[width=0.8\textwidth]{so_bravo_90perc_10^4/sprob_first_three.png}\caption{
This plot shows, for each state margin, when the underlying election is as announced, the number of SO \BRAVO audits that stopped in the $j^{th}$ round,
as a fraction of all EoR \BRAVO audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$.}
\label{fig:so_bravo_sprob}
\end{figure}

Figure~\ref{fig:minerva1_sprob} and Figure~\ref{fig:minerva1p5_sprob} show the same proportions for \Minerva round multipliers of $1.0$ and $1.5$ respectively. We see that the first round size estimates were fairly accurate, with first round stopping probabilities being very close to $90\%$. For subsequent rounds, the multipliers of $1.0$ and $1.5$ respectively achieved smaller stopping probabilities, as the $1.0$ multiplier was not chosen so as to obtain $\chi_j({\mathcal A}) = 0.9$, and the $1.5$ multiplier is a very rough estimate. Note that we chose a simple multiplier for future rounds, but one could make more accurate round size estimates before the audit begins.

\begin{figure}
\includegraphics[width=0.8\textwidth]{minerva_multiround_1x_10^4/sprobs_first_three.png}
\caption{This plot shows, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$ and round size multiple of $1.0$.}
\label{fig:minerva1_sprob}
\end{figure}

\begin{figure}
\includegraphics[width=0.8\textwidth]{minerva_multiround_1p5x_10^4/sprobs_first_three.png}
\caption{This plot shows, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$ and round size multiple of $1.5$.}
\label{fig:minerva1p5_sprob}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{bravo_risks_same_plot.png}
\caption{This plot shows the fraction of EoR \BRAVO audits (all states with margins at least $0.05$) and SO \BRAVO audits (the 13 states for which our simulations are complete so far) that stopped in any of the $5$ rounds when the underlying election was a tie.}
\label{fig:bravo_risk}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{minerva_multiround_1x_10^4/total_risk.png}
\caption{This plot shows, for each state margin,
the fraction of \Minerva audits with a round size multiple of $1.0$ that stopped in any of the $5$ rounds when the underlying election was a tie.}
\label{fig:minerva1_risk}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{minerva_multiround_1p5x_10^4/total_risk.png}
\caption{This plot shows, for each state margin,
the fraction of \Minerva audits with a round size multiple of $1.5$ that stopped in any of the $5$ rounds when the underlying election was a tie.}
\label{fig:minerva1p5_risk}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.8\textwidth]{eor_bravo_90perc_10^4_corrected/sprob_first_three_cropped.png}\caption{
This plot shows, for each state margin, when the underlying election is as announced, the number of EoR \BRAVO audits that stopped in the $j^{th}$ round,
as a fraction of all EoR \BRAVO audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$.}
\label{fig:eor_bravo_sprob}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.8\textwidth]{so_bravo_90perc_10^4/sprob_first_three.png}\caption{
This plot shows, for each state margin, when the underlying election is as announced, the number of SO \BRAVO audits that stopped in the $j^{th}$ round,
as a fraction of all EoR \BRAVO audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$.}
\label{fig:so_bravo_sprob}
\end{centering}
\end{figure}

Figure~\ref{fig:minerva1_sprob} and Figure~\ref{fig:minerva1p5_sprob} show the same proportions for \Minerva round multipliers of $1.0$ and $1.5$ respectively. We see that the first round size estimates were fairly accurate, with first round stopping probabilities being very close to $.9$. For subsequent rounds, the multipliers of $1.0$ and $1.5$ respectively achieved smaller stopping probabilities, as the $1.0$ multiplier was not chosen so as to obtain $\chi_j({\mathcal A}) = 0.9$, and the $1.5$ multiplier is a very rough estimate. Note that we chose a simple multiplier for future rounds, but one could make more accurate round size estimates before the audit begins.

\begin{figure}
\begin{centering}
\includegraphics[width=0.8\textwidth]{minerva_multiround_1x_10^4/sprobs_first_three.png}
\caption{This plot shows, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$ and round size multiple of $1.0$.}
\label{fig:minerva1_sprob}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.8\textwidth]{minerva_multiround_1p5x_10^4/sprobs_first_three.png}
\caption{This plot shows, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$ and round size multiple of $1.5$.}
\label{fig:minerva1p5_sprob}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.6\textwidth]{bravo_risks_same_plot.png}
\caption{This plot shows the fraction of EoR \BRAVO audits (all states with margins at least $0.05$) and SO \BRAVO audits (the 13 states for which our simulations are complete so far) that stopped in any of the $5$ rounds when the underlying election was a tie.}
\label{fig:bravo_risk}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.6\textwidth]{minerva_multiround_1x_10^4/total_risk.png}
\caption{This plot shows, for each state margin,
the fraction of \Minerva audits with a round size multiple of $1.0$ that stopped in any of the $5$ rounds when the underlying election was a tie.}
\label{fig:minerva1_risk}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.6\textwidth]{minerva_multiround_1p5x_10^4/total_risk.png}
\caption{This plot shows, for each state margin,
the fraction of \Minerva audits with a round size multiple of $1.5$ that stopped in any of the $5$ rounds when the underlying election was a tie.}
\label{fig:minerva1p5_risk}
\end{centering}
\end{figure}
